---
title             : "The role of translation equivalents in bilingual word learning"
shorttitle        : "Translation equivalents"

author: 
  - name          : "Alvin W. M. Tan"
    affiliation   : "1"
    corresponding : yes
    address       : "450 Jane Stanford Way, Building 420, Stanford University, Stanford, CA 94305"
    email         : "tanawm@stanford.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Methodology"
      - "Formal Analysis"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Virginia A. Marchman"
    affiliation   : "1"
    role:
      - "Writing - Review & Editing"
      - "Supervision"
  - name          : "Michael C. Frank"
    affiliation   : "1"
    role:
      - "Conceptualization"
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Stanford University"

authornote: |
  Alvin W. M. Tan, Department of Psychology, Stanford University, ORCID 0000-0001-5551-7507.
  Virginia A. Marchman, Department of Psychology, Stanford University, ORCID 0000-0001-7183-6743.
  Michael C. Frank, Department of Psychology, Stanford University, ORCID 0000-0002-7551-4378.

abstract          : "(ref:abstract)"
  
keywords          : "translation equivalents, bilingualism, word learning, standard model, baseline problem"
# wordcount         : "X"

bibliography      : "index/bib/thesis.bib"
annotate_references: no

floatsintext      : no
linenumbers       : no
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

mainfont          : "CMU Serif"

classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library(papaja)
library(glue)
library(Matrix)
library(tidyverse)
library(here)
library(kableExtra)
library(broom.mixed)
library(lme4)
library(colorspace)
library(corrplot)
r_refs("r-references.bib")
knitr::opts_knit$set(root.dir = './')
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  error = FALSE,
  echo = FALSE,
  dev = "cairo_pdf")
extrafont::loadfonts()
walk(list.files("scripts", pattern = "*.R$", full.names = TRUE), source)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

(ref:abstract) Bilingual environments present an important context for word learning. One feature of bilingual environments is the existence of translation equivalents (TEs)---words in different languages that share similar meanings. Understanding patterns of TEs learning over development may give us insight into mechanisms underlying word learning in young children. However, prior studies of TE learning have often been confounded by the fact that increases in overall vocabulary size with age lead to greater opportunities for learning TEs. To address this confound, we employed an item-level analysis, which controls for the age trajectory of each item independently. We used Communicative Development Inventory data from four bilingual datasets (two English--Spanish and two English--French; total $N$ = 484) for modelling. Results indicated that knowing a word's TE increased the likelihood of knowing that word for younger children and for TEs that are more similar phonologically. These effects were consistent across datasets, but varied across item lexical categories. Thus, TEs may allow bilingual children to bootstrap their early word learning in one language using their knowledge of the other language.

<!-- We used `r cite_r("r-references.bib")` for all our analyses. -->

```{r child = "index/01-introduction.Rmd"}
```

```{r child = "index/02-study.Rmd"}
```

```{r child = "index/03-discussion.Rmd"}
```

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
